article title

### 2022-07-24 pilon_gilles_glossary.tex
Fix typos
Add chi-square distribution
Add distance to target
Add process behaviour chart

@@

@@

@@

\newglossaryentry(type_i_error},

@@

\newglossaryentry(type_ii_error},

@@

>>>>

\newglossaryentry{chi_square_distribution}
    name={chi-square distribution},
    description={It is the distribution of a sum of the squares of k independent standard normal random variables with k degrees of freedom.},
    plural={chi-square distributions}

@@

\newglossaryentry{distance_to_target}
    name={distance to target},
    description={The difference between the specification target and the average is the difference you must adjust to aim the process correctly.}

@@

\newglossaryentry{process_behaviour_chart}
    name={process behaviour chart},
    description={It is used to determine if the variation of a sample statistic of a process is stable and predictable, that is, in a state of statistical control. It is also called a Shewhart chart and a control chart.}
    plural={process behaviour charts}

@@

\newglossaryentry{type_i_error}

@@

\newglossaryentry{type_ii_error}

@@

    plural={Type II errors}
